---
title: "P8104 HW 1 LEL2176"
output: github_document
---

# Problem 1
```{r}
#load in library and dataset
library(tidyverse)
library(moderndive)
data("early_january_weather")
```

the variables in this data set include `r origin`, `r year`, `r month`, `r day`,
`r hour`, `r temp`, `r dewp`, `r humid`, `r humid`, `r wind_dir`, `r wind_speed`,
`r wind_gust`, `r precip`, `r pressure`, `r visib`. the size of the data set is:
`r nrow(358)` and `r ncol(15)`. the mean temperature of the data is: 
`r mean(early_january_weather[["temp]]` which is equal to 39.58212.

```{r}
weather_scat = ggplot(early_january_weather, aes(x = time_hour, y  = temp, color = "humid")) + geom_point()
ggsave("weather_scat.pdf")
```

the scatter plot `r weather_scat` shows the relationship between time measure by
hours and the recorded temperature. when analyzing the graph there is a clear
sinusoidal wave pattern that repeats everyday. these waves represents the highs and
lows of daily temperature with the temperature peaking midday and dropping during
the night when the sun is gone. however, the overall trend of the line has an 
increasing slope showing that the temperature is slowly increasing as the days go
on.

# Problem 2
